Efficient Parallelization of $\ell_1$-Minimization for Face Recognition \thanks{Corresponding author: . This work was partially supported by ARO MURI W911NF-06-1-0076.}

### 2011-02-11 paper/main.tex
minor change

Past work in parallelizing $\ell_1$-minimization has been limited.  Murphy at UCB implemented the L1-Spirit algorithm on Nvidia GPUs for MRI reconstruction and Borghi at UCLA developed a proximal point algorithm using Moreau-Yosida regularization, which is special form of the $\ell_1$-minimization based on proximal gradient.

@@

The augmented lagrange multiplier (ALM) method utilizes a popular class of convex techniques, the lagrange multiplier, solving the problem:
\begin{equation}
F(x) = f(x) + \lambda g(x).
\end{equation}
which can be formulated as an augmented Langrange function given by
\begin{equation}
L_u(x,y) = \|x\|_1 + <\y, b - A\x - \e> + \frac{\mu}2 \| b-A\x-\e \|_2^2
\end{equation}

@@

>>>>

Past work in parallelizing $\ell_1$-minimization has been limited.  In 2009, Murphy at UCB implemented the L1-Spirit algorithm on Nvidia GPUs for MRI reconstruction and in 2009 Borghi at UCLA developed a proximal point algorithm using Moreau-Yosida regularization, which is special form of the $\ell_1$-minimization based on proximal gradient.

@@

The augmented lagrange multiplier (ALM) method utilizes a popular class of convex techniques, the lagrange multiplier, solving the problem:
\begin{equation}
F(x) = f(x) + \lambda g(x).
\end{equation}
which can be formulated as an augmented Lagrange function given by
\begin{equation}
L_u(x,y) = \|x\|_1 + <\y, b - A\x - \e> + \frac{\mu}2 \| b-A\x-\e \|_2^2
\end{equation}

@@

In order to adapt the general algorithm to face alignment and recognition, we formulated the 
$\ell_1$-minimization problem as ___ as described in [book].
